Mapping Microblog Posts to Encyclopedia Articles

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex

The implemented
system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
the twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
document semantically describing the most recent twitter posts matching the
given query. The returned RDF document furthermore contains a mapping of the
query to Encyclopedia articles which based on the content published by users that most recently used the search
term in their posts maps to articles best describing the content of Twitter
messages related to the term. An overview of the System Architecture is given in Figure
\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
Twitter Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}). We will follow those steps along a simple example, using
\#ka (a hashtag frequently used to describe posts related to the city of
Karlsruhe, Germany) as search term for the Twitter Search wrapper.

@@

% 1. Schicke Suchanfrage an Twitter Search API
% Ich würde etwas ausführlicher erklären, was die Twitter Search API macht (an welcher Stelle im Paper müsste man nochmal überlegen).
% 2. Greife Ergebnisse ab

@@

the output RDF document containes the following triples to reference the DBPedia
mappings:\newline\linebreak \texttt{<rdfs:seeAlso

>>>>

The implemented
system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
the Twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
document semantically describing the most recent Twitter messages matching the
given query. The returned RDF document furthermore contains a mapping of the
query to Encyclopedia articles which based on the content published by users that most recently used the search
term in their posts maps to articles best describing the content of Twitter
messages related to the term. An overview of the System Architecture is given in Figure
\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
Twitter Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}). We will follow those steps along a simple example, using
\#ka (a hashtag frequently used to describe posts related to the city of
Karlsruhe, Germany) as search term for the Twitter Search wrapper.

@@

@@

the output RDF document containes the following triples to reference the
DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
